### 2019-08-07 initial/notes.tex
temp checkpoint

>>>>

Now, this turns out to be slightly inaccurate for $f > 0$ simply because our
$\mu_{sep}$ approximation is not so accurate for $\eta \gtrsim 0.2$, where the
top leg is significantly lower than the symmetric $\mu_{sep} = \eta \cos I \pm
\dots$ would predict. This would mean the two legs don't cancel as exactly, and
the capture probability increases, which is observed.
